Deep Learning \\ NATURE Review Article

### 2014-11-01 2014/nature-review/Deep-Learning-Nature-Review.tex

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{times}
\usepackage{url}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

@@

\begin{verbatim}
We plan to organize this review chronologically, but with forward looking
 comments. We will start with the excitement over the backpropagation
 learning algorithm for multilayer neural networks in the 1980's and
 explain why these networks did not live up to the very high expectations
 that people had for them.  Given our current knowledge, the real reasons
 for the disappointments of the 1990's are now clear: people radically
 underestimated the amount of data and the amount of computation that were
 required to demonstrate the power of this type of learning algorithm.
\end{verbatim}

@@

The kind of representations extracted by deep learning have two central
characteristics: they are distributed representations and they are deep
representations. A distributed representation is composed of features that
are not mutually exclusive, such that the number of configurations of
values of these features grows exponentially with the number of
features. Imagine for example that these features are binary, i.e., each
can take only one of two values. Then up to configurations of these bits
are possible, thus carving up to regions in the input space. Yet the number
of free parameters required to carve this very rich partition of the input
space grows only linearly with , since feature (e.g., a neuron) comes with
its set of parameters (e.g., synaptic weights into the neuron). This is in
contrast with the majority of other machine learning approaches, in which
the number of parameters (and thus of examples) necessary to distinguish
input regions grows linearly with , instead of logarithmically. This
includes most clustering techniques, nearest-neighbor techniques, most
kernel-based non-parametric approaches, and decision trees. These
approaches can be plagued by the curse of
dimensionality~\citep{Bengio-localfailure-NIPS-2006-small,Bengio-decision-trees10}:
in rich domains such as images and text, the number of configurations of
interest of the observed variables is exponentially large, making it very
difficult to generalize. As argued in \citet{Bengio-book, Montufar+Morton-2014, Montufar-et-al-NIPS2014},
distributed representations potentially have a very large
statistical advantage, in the sense that fewer examples might be needed to
achieve the same ability to generalize to new cases, or that markedly
better generalization can be obtained for the same number of training
examples.

@@

\begin{verbatim}
We will explain the core issue of hand-engineering features versus learning
 features automatically from data and show how backpropagation learns
 features. We will describe the most successful application of the
 80's/90's which was reading hand-written digits. We will also explain
 "distributed representations[a]" and illustrate them by showing how
 backpropagation can be used to convert words to vectors of meaningful
 features which are now very widely used in natural language applications.
  We will show how backpropagation through time can be used to learn
 recurrent neural networks and we will explain the vanishing/exploding
 gradients problem that makes this type of learning difficult.
\end{verbatim}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=0.7\linewidth]{fig-hidden-recurrence-rnn.png}}
\caption{(a better figure can be made)}
\end{figure}

@@

The challenge of training very deep nets and recurrent networks over long sequences

@@

\begin{verbatim}
We will explain the breakthrough that occurred in 2006 when an effective
 new way of learning multiple layers of features was discovered. The idea
 is to learn the layers one a time with the objective being to build a good
 model of the correlations between feature activities in the previous layer
 (or the input).  After this layer-by-layer unsupervised "pre-training" to
 discover features, backpropagation works very well for fine-tuning the
 features that have already been discovered.  Will we describe several
 variations of the pre-training methods.
\end{verbatim}

@@

\begin{verbatim}
We will explain the acoustic modeling problem in speech recognition and
 desribe how initial results in 2009 using pre-training on the TIMIT
 dataset led to huge improvement in acoustic modeling over the next few
 years. Acoustic models based on deep neural networks are now used in most
 smart phones.  We will address the issue of when pre-training is needed
 and when it is unneccessary.
\end{verbatim}

@@

Convolutional capsules (just a couple of sentences).

PROVISIONAL LIST OF FIGURES, TABLES AND BOXES

One box explaining the backpropagation algorithm for computing error derivatives.

@@

KEY REFERENCES (dotted lines separate refs for each heading above)
(some of the conference papers here are awaiting review as journal papers and those refs will be updated if accepted.)

@@

\bibliography{strings,strings-shorter,ml,aigaion}
\bibliographystyle{natbib}

>>>>

\documentclass[11pt]{article} % For LaTeX2e
\usepackage{times}
\usepackage{url}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}

\addtolength{\textwidth}{2cm}
%\addtolength{\textwidth}{1cm}
\addtolength{\textheight}{2cm}
%\addtolength{\textheight}{1cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}

@@

{\em 
We plan to organize this review chronologically, but with forward looking
 comments. We will start with the excitement over the backpropagation
 learning algorithm for multilayer neural networks in the 1980's and
 explain why these networks did not live up to the very high expectations
 that people had for them.  Given our current knowledge, the real reasons
 for the disappointments of the 1990's are now clear: people radically
 underestimated the amount of data and the amount of computation that were
 required to demonstrate the power of this type of learning algorithm.
}

@@

The kind of representations extracted by deep learning have two central
characteristics: they are distributed representations and they are deep
representations. A distributed representation is composed of features that
are not mutually exclusive, such that the number of configurations of
values of these features grows exponentially with the number of
features. Imagine for example that these features are binary, i.e., each
can take only one of two values. Then up to configurations of these bits
are possible, thus carving up to regions in the input space. Yet the number
of free parameters required to carve this very rich partition of the input
space grows only linearly with , since feature (e.g., a neuron) comes with
its set of parameters (e.g., synaptic weights into the neuron). This is in
contrast with the majority of other machine learning approaches, in which
the number of parameters (and thus of examples) necessary to distinguish
input regions grows linearly with , instead of logarithmically. This
includes most clustering techniques, nearest-neighbor techniques, most
kernel-based non-parametric approaches, and decision trees. These
approaches can be plagued by the curse of
dimensionality~\citep{Bengio-localfailure-NIPS-2006-small,Bengio-decision-trees10}:
in rich domains such as images and text, the number of configurations of
interest of the observed variables is exponentially large, making it very
difficult to generalize. As argued in \citet{Bengio-book-2009,Montufar+Morton-2014,Montufar-et-al-NIPS2014},
distributed representations potentially have a very large
statistical advantage, in the sense that fewer examples might be needed to
achieve the same ability to generalize to new cases, or that markedly
better generalization can be obtained for the same number of training
examples.

@@

{\em 
We will explain the core issue of hand-engineering features versus learning
 features automatically from data and show how backpropagation learns
 features. We will describe the most successful application of the
 80's/90's which was reading hand-written digits. We will also explain
 "distributed representations[a]" and illustrate them by showing how
 backpropagation can be used to convert words to vectors of meaningful
 features which are now very widely used in natural language applications.
  We will show how backpropagation through time can be used to learn
 recurrent neural networks and we will explain the vanishing/exploding
 gradients problem that makes this type of learning difficult.
}

@@

\iffalse
\begin{figure}[H]
\centerline{\includegraphics[width=0.7\linewidth]{fig-hidden-recurrence-rnn.png}}
\caption{(a better figure can be made)}
\end{figure}
\fi

@@

\subsection{The challenge of training very deep nets and recurrent networks over long sequences}

@@

{\em
We will explain the breakthrough that occurred in 2006 when an effective
 new way of learning multiple layers of features was discovered. The idea
 is to learn the layers one a time with the objective being to build a good
 model of the correlations between feature activities in the previous layer
 (or the input).  After this layer-by-layer unsupervised "pre-training" to
 discover features, backpropagation works very well for fine-tuning the
 features that have already been discovered.  Will we describe several
 variations of the pre-training methods.
}

@@

{\em We will explain the acoustic modeling problem in speech recognition and
 desribe how initial results in 2009 using pre-training on the TIMIT
 dataset led to huge improvement in acoustic modeling over the next few
 years. Acoustic models based on deep neural networks are now used in most
 smart phones.  We will address the issue of when pre-training is needed
 and when it is unneccessary.
}

@@

Convolutional capsules (just a couple of sentences).\\

{\bf PROVISIONAL LIST OF FIGURES, TABLES AND BOXES}

In addition to the above:\\

One box explaining the backpropagation algorithm for computing error derivatives.\\

@@

{\bf KEY REFERENCES (dotted lines separate refs for each heading above)}\\
(some of the conference papers here are awaiting review as journal papers and those refs will be updated if accepted.)

@@

\bibliography{strings,ml,aigaion}
\bibliographystyle{natbib}
